Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
handle Alessandro's comments
Wording/grammar

\begin{abstract}
This work presents a sound and automated approach to synthesise 
digital feedback control architectures for physical plants represented 
as linear, time invariant models. Models are encompassed by dynamical 
equations with inputs, evolving over a continuous state space describing 
the evolution of the physical variables of the system.  The approach is divided 
in two main parts, brought together by a counter-example guided inductive 
synthesis (CEGIS) loop, as follows. First, we devise a static feedback controller 
that stabilises the system; then, we verify its potential safety by means of either 
of the following approaches: forward reachability analysis via unfolding of the dynamics, 
or invariant set generation via abstract acceleration;  
further, if the above step fails, we loop back and invoke a CEGIS call 
to seek alternative stabilising feedbacks, benefiting from the obtained counter-examples 
to safety. 
\textcolor{red}{[Mention GA \todo{GA? Genetic Algorithms? We don't use GA?} and Abstract Acceleration here?]}

@@

Linear Time Invariant (LTI) control models represent a broad class of dynamical systems
%modern embedded software, performing highly non-trivial control tasks,
with significant impact in numerous application areas such as
the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
Control synthesis for LTI is a broadly investigated, 
however the presence of digital control architectures is exacerbated by specific artefacts,  
%specific to digital control, 
such as the effects of finite-precision arithmetic, time discretization, and quantisation noise, which are typically introduced 
by Analogue-to-Digital (A/D) and Digital-to-Analogue (D/A) conversion.  
Whilst the research on digital control is well developed~\cite{astrom1997computer}, 
automated and sound control synthesis is a challenging task. 
%Thus, the programming is a key barrier to broad adoption of digital control, 
%and requires considerable expertise.

Whilst there is a vast literature in validation of control systems,
the subject of control synthesis has been somewhat restricted in the
properties it explores.  Traditionally, this focuses mainly on the
subject of stability %, working typically on continuous domains
\cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.
Reachability tools are
also used when discretising the state-space for both verification and
parametric synthesis~\cite{cimatti2013parameter}.

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous domain of the plant, 
alongside the discrete domain of the controller and the hybrid elements that relate them.  
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
Due to the complexity of such systems, in this particular work we focus
on linear models \addtodo{[clarify next] with known configurations} and perform parametric synthesis
of safe digital controllers.

>>>>

\begin{abstract}
This work presents a sound and automated approach to synthesise 
digital feedback control architectures for physical plants represented 
as linear, time invariant models. Models are encompassed by dynamical 
equations with inputs, evolving over a continuous state space describing 
the evolution of the physical variables of the system.  The approach is divided 
in two main parts, brought together by a counter-example guided inductive 
synthesis (CEGIS) loop, as follows. First, we devise a static feedback controller 
that stabilises the system; then, we verify its potential safety by means of either 
of the following approaches: forward reachability analysis via unfolding of the dynamics, 
or invariant set generation via abstract acceleration;  
further, if the above step fails, we loop back and invoke a CEGIS call 
to seek alternative stabilising feedbacks, benefiting from the obtained counter-examples 
to safety. 
\textcolor{red}{[Mention GA \todo{GA? Genetic Algorithms? We don't use GA?} and Abstract Acceleration here? Alessandro: we are not using GA. We don't think that we should describe it here.]}

@@

Linear Time Invariant (LTI) control models represent a broad class of dynamical systems
%modern embedded software, performing highly non-trivial control tasks,
with significant impact in numerous application areas such as
the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
Control synthesis for LTI is broadly investigated, 
however the use of digital control architectures adds new challenges due to 
%exacerbated by specific artefacts,  
the effects of finite-precision arithmetic, time discretization, and quantisation noise, which are typically introduced 
by Analogue-to-Digital (A/D) and Digital-to-Analogue (D/A) conversion.  
Whilst the research on digital control is well developed~\cite{astrom1997computer}, 
automated and sound control synthesis is a challenging task. 
%Thus, the programming is a key barrier to broad adoption of digital control, 
%and requires considerable expertise.

Whilst there is a vast literature on validation of control systems,
the subject of control synthesis has been somewhat restricted in the
properties it explores.  Traditionally, this focuses mainly on the
subject of stability %, working typically on continuous domains
\cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.
Reachability tools are
also used when discretizing the state-space for both verification and
parametric synthesis~\cite{cimatti2013parameter}.

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous domain of the plant, 
alongside the discrete domain of the controller and the hybrid elements that relate them.  
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
Due to the complexity of such systems, in this particular work we focus
on linear models %\addtodo{[clarify next] with known configurations} 
and perform parametric synthesis
of safe digital controllers.
